---
title: "Build Many Element With data.frame"
---

If small amount of nodes / edges are needed to be plotted, using `buildNode` and `buildEdge` will fine. However in most case, almost ~ 100 element or more should be plotted.

Which is not efficient with repetitive using of `buildNode` and `buildEdge`.

`buildElem` is function for that case, which build uniform elements(only `node` or only `edge`).


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyCyJS)
```

These 2 code will return same results. (nevermind layout, it contains randomness)

```{r}
  shinyCyJS(list(
    buildNode('a'),
    buildNode('b', width = 20),
    buildNode('c', width = 30),
    buildNode('d', width = 40),
    buildEdge('a','b'),
    buildEdge('a','c'),
    buildEdge('c','d'),
    buildEdge('b','d')
    ))
```


```{r}
  a = data.frame(
    id = c('a','b','c','d'),
    width = c(15,20,30,40)
  )

  b = data.frame(
    source = c('a','a','c','b'),
    target = c('b','c','d','d')
  )

  nodes = buildElems(a,'Node')
  edges = buildElems(b,'Edge')

  shinyCyJS(c(nodes, edges))
```
